### 2015-05-27 writing/SNLI paper/abstract.tex
Pre workshopping cleanup.
Comments from KST and Ignacio.

\begin{abstract} 
  % Entailment and contradiction are fundamental to natural language
  % meaning and lie at the heart of tasks like summarization, textual
  % entailment, and commonsense reasoning.
  Entailment and contradiction are fundamental to natural language
  meaning and so have emerged (in the form of tasks involving
  reasoning, inference, and summarization) as an important testing
  ground for semantic representations.
  %
  %However, computational modeling of these concepts is currently
  %hampered by the limited nature of existing annotated resources.
  However, progess is currently hampered by the limitations of
  existing annotated resources.
  %
  To address this, we present a new corpus of sentence pairs labeled
  for entailment, contradiction, and semantic independence. At 570K
  pairs, it is orders of magnitude larger than all other resources
  of its type.
  %
  And, in contrast to many such resources, all of the sentences were
  written by humans in a grounded, naturalistic context, and 54K of
  the labels have been independently validated.
  %
  In this paper, we use this corpus to evaluate a wide variety of
  models for natural language inference, finding that Tree-Structured
  Long Short-Term Memory networks (TreeLSTMs) achieve the best
  performance.
  %
  In addition, to enhance the case for TreeLSTMs, and deepen the
  argument for the centrality of entailment and contradiction in
  semantics, we show that the TreeLSTM's representatations, trained on
  our corpus, perform well in a disparate set of additional semantic
  tasks.  
  \todo{Structure more around results (vs. data).}
\end{abstract}

>>>>

\begin{abstract} 
  % Entailment and contradiction are fundamental to natural language
  % meaning and lie at the heart of tasks like summarization, textual
  % entailment, and commonsense reasoning.
  Entailment and contradiction are fundamental to natural language
  meaning and so have emerged (in the form of tasks involving
  reasoning, inference, and summarization) as an important testing
  ground for semantic representations.
  %
  %However, computational modeling of these concepts is currently
  %hampered by the limited nature of existing annotated resources.
  However, progress is currently hampered by the limitations of
  existing annotated resources.
  %
  To address this, we present a new corpus of sentence pairs labeled
  for entailment, contradiction, and semantic independence. At 570K
  pairs, it is orders of magnitude larger than all other resources
  of its type.
  %
  And, in contrast to many such resources, all of the sentences were
  written by humans in a grounded, naturalistic context.
  %
  In this paper, we use this corpus to evaluate a wide variety of
  models for natural language inference, finding that Tree-Structured
  Long Short-Term Memory networks (TreeLSTMs) achieve the best
  performance.
  %
  In addition, to enhance the case for TreeLSTMs, and deepen the
  argument for the centrality of entailment and contradiction in
  semantics, we show that the TreeLSTM's representations, trained on
  our corpus, perform well in a disparate set of additional semantic
  tasks.  
  \todo{Structure more around results (vs. data).}
\end{abstract}

### 2015-05-27 writing/SNLI paper/corpus.tex
Comments from KST and Ignacio.

@@

@@

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
\multicolumn{2}{l}{\textbf{Data set sizes:}}\\
Training pairs &  550,152\\
Development pairs &  10,000\\
Test pairs & 10,000\\
\midrule
\multicolumn{2}{l}{\textbf{Sentence length:}}\\
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
\multicolumn{2}{l}{\textbf{Frequency of complete sentences:}}\\
Premise `S'-rooted parses & 74.0\%\\
Hypothesis `S'-rooted parses & 88.9\%\\
    \bottomrule
  \end{tabular}
% From 1.0rc3
\caption{\label{collection-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report some statistics for both.} 
\end{table}

@@

\noindent\todo{Update as appropriate (CM)}

>>>>

\noindent\todo{Introduce name of corpus.}

@@

\noindent\todo{Explain our 5x->1x annotation switch...}

@@

\noindent\todo{More on *why* `-' isn't a valid test label}

@@

\begin{table}
\center
  %\setlength{\tabcolsep}{15pt}
  %\renewcommand{\arraystretch}{1.2}
  \begin{tabular}{l l} 
    \toprule
\multicolumn{2}{l}{\textbf{Data set sizes:}}\\
Training pairs &  550,152\\
Development pairs &  10,000\\
Test pairs & 10,000\\
\midrule
\multicolumn{2}{l}{\textbf{Sentence length:}}\\
Premise mean token count & 14.1\\
Hypothesis mean token count & 8.3 \\
\midrule
\multicolumn{2}{l}{\textbf{Parser output:}}\\
Premise `S'-rooted parses & 74.0\%\\
Hypothesis `S'-rooted parses & 88.9\%\\
Unique word tokens (ignoring case) & ...\\
    \bottomrule
  \end{tabular}
% From 1.0rc3
\todo{Unique word count.}
\caption{\label{collection-stats}Key statistics for the raw sentence pairs. Since the two halves of each pair were collected separately, we report some statistics for both.} 
\end{table}

@@

\noindent\todo{Use version number for 4/20/15 model}

### 2015-05-27 writing/SNLI paper/transfer.tex
Bit more cleanup.
Comments from KST and Ignacio.

@@

The final column shows the state of the art results from \cite{lai2014illinois}, \cite{zhao2015self}, \cite{tai2015improved}, TODO, respectively.
\noindent\todo{Does Tai have the SotA on SST?}

The results are shown in Table~\ref{tab:transferresults}. For each task, the transfer model is compared with a model that was initialized randomly as normal. Note that \todo{something interesting happens}. Within the domain of NLI, our transfer model shows the best number yet reported on SICK for a fully-learned model, and approaches the overall state of the art (and to the 84\% level of interannotator agreement, a likely performance cieling), while the randomly initialized model performs poorly. This suggests that the introduction of SNLI makes it newly possible to train representation learning models for sentence meaning of a level of quality that is competitive with the best hand-engineered models on semantically sophisticated tasks.

>>>>

\noindent\todo{Mention domain limitation to scenes}

@@

The final column shows the state of the art results from \citealt{lai2014illinois}, \citealt{zhao2015self}, \citealt{tai2015improved}, and \todo{CITE}.
\noindent\todo{Does Tai have the SotA on SST?}

The results are shown in Table~\ref{tab:transferresults}. For each task, the transfer model is compared with a model that was initialized randomly as normal. Note that \todo{something interesting happens}. Within the domain of NLI, our transfer model shows the best number yet reported on SICK for a fully-learned model, and approaches the overall state of the art (and to the 84\% level of interannotator agreement, a likely performance ceiling), while the randomly initialized model performs poorly. This suggests that the introduction of SNLI makes it newly possible to train representation learning models for sentence meaning of a level of quality that is competitive with the best hand-engineered models on semantically sophisticated tasks.
